### 2017-04-19 thesis/latex/thesis.tex

\subsubsection{Why is dynein special and interesting?}
Compare the processive motion of dynein to kinesin in \textbf{a.)} directionality, \textbf{b.)} stepping pattern and \textbf{c.)} size (like how it can step over roadblocks kinesin cannot).\\

Talk about why a random stepping motor is interesting compared to a orderly-stepping motor: what is different about dynein's structure that makes it step differently? Compare the crystal structures and ask lots of questions. Build interest in the motors here.\\

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
%%   \caption{Crystal structures of cytoplasmic dynein 1 and kinesin KIF5B (PDB IDs 4RH7 and 1BG2).}
%%   \label{kin_n_dyn}
%% \end{figure}

\textit{make this figure good -- find a full length kinesin crystal structure, not 1BG2. Use kindyn.pse as a template.}

>>>>

\subsubsection{Why is dynein interesting?}
Studying how nature creates directed motion is interesting in itself. Another interesting question is how, given the large number of similarities between motors kinesin and dynein, does dynein achieve such a radically different stepping pattern than kinesin? Elucidating how the structural differences between the motors give rise to the differences in dynamics would provide lots of important information on how the machines fine-tune their stepping.\\

The major difference between kinesin and dynein is their size. Kinesin proteins are generally 100-200 kD in mass, whereas dynein is roughly 1mD. As shown in Figure \ref{fig:kinesin-vs-dynein}, the size and volume differences between proteins is very apparent. Dynein is about 20nm from MTBD to tail, whereas kinesin is ----. Another key difference is the separation between active sites on either protein. Kinesin binds to the MT with a foot domain, colored blue in Figure \ref{fig:kinesin-vs-dynein}. It hydrolyzes ATP at the residues colored pink. The separation between these domains is roughly ---nm. In contrast, Dynein binds to the MT with its MTBD, colored blue, and hydrolyses ATP in its motor domain, residues colored pink. This distance is close to 20nm in length - much longer than kinesin. Another difference is the way the motors interact with the microtubule. Both motors bind to the MT using domains. However, for dynein the motor-MTBD-MT angle is ---, whereas for kinesin, it is ---.\\

Despite these differences, the two motors implement very similar chemical cycles to achieve motion. Both motors begin bound to the microtubule, then bind ATP, causing them to lift one foot off. They then hydrolyse the ATP, causing their feet to kick forward and rebind. They then

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/kinesin-vs-dynein}
%%   \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}.}
%%   \label{fig:kinesin-vs-dynein}
%% \end{figure}
